New lower bounds for Schur and weak Schur numbers

### 2022-06-23 article_schur/article.tex
intro

\documentclass[review,onefignum,onetabnum]{siamart190516}

\usepackage{amssymb}
\usepackage{dsfont}
\usepackage{MyMnSymbol}

\usepackage{float}

\usepackage{nicematrix}

\newsiamremark{remark}{Remark}

@@

\title{New lower bounds for Schur and weak Schur numbers \thanks{Submitted to the editors 02/24/2022.}}

\author{Romain Ageron\thanks{CentraleSup\'elec, Universit\'e{} Paris-Saclay, Gif-sur-Yvette, France
	(\email{romain.ageron@student-cs.fr}, \email{paul.casteras@student-cs.fr},
	\email{thibaut.pellerin@student-cs.fr}, \email{yann.portella@student-cs.fr}).}
\and Paul Casteras\footnotemark[2]
\and Thibaut Pellerin\footnotemark[2]
\and Yann Portella\footnotemark[2]
\and Arpad Rimmel\footnotemark[2]\ \thanks{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, Orsay, France
	(\email{arpad.rimmel@centralesupelec.fr}).}
\and Joanna Tomasik\footnotemark[2]\ \footnotemark[3]\ \thanks{Corresponding author
	(\email{joanna.tomasik@centralesupelec.fr}).}}

\headers{New lower bounds for Schur and weak Schur numbers}{R. Ageron, P. Casteras,
T. Pellerin, Y. Portella, A. Rimmel, J. Tomasik}

\begin{document}
\maketitle

@@

\begin{keywords}
	Schur number, Weak Schur number, Ramsey theory, Sum-free partition
\end{keywords}

\begin{AMS}
	05D10, 11P81, 05A17, 11B75
\end{AMS}

@@

\begin{table}[tbhp]
{\footnotesize
	\caption{Comparison of lower bounds for Schur numbers}\label{table:1}
\begin{center}
	\begin{small}
	\setlength{\tabcolsep}{3pt}
	\renewcommand{\arraystretch}{1.2}
	\begin{NiceTabular}{*{13}{c}}[vlines]
	\CodeBefore
		\cellcolor{gray!40}{2-2}
		\cellcolor{gray!40}{2-3}
		\cellcolor{gray!40}{2-4}
		\cellcolor{gray!40}{2-5}
		\cellcolor{gray!40}{2-6}
		\cellcolor{gray!40}{3-2}
		\cellcolor{gray!40}{3-3}
		\cellcolor{gray!40}{3-4}
		\cellcolor{gray!40}{3-5}
		\cellcolor{gray!40}{3-6}
	\Body
		\hline
		\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
		\hline
		\Block{2-1}{State of the art} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,696 & 5\,286 & 17\,694 & 60\,320 & 201\,696 & 637\,856 \\
		& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{rowley2021improved} & \cite{RowleyRamsey} & \cite{RowleyRamsey} &
			\cite{RowleyRamsey} & \cite{RowleyRamsey} & \cite{RowleyRamsey} \\
		\hline
		\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{644\,628} \\
		\hline
	\end{NiceTabular}
	\end{small}
\end{center}
}
\end{table}

\begin{table}[tbhp]
{\footnotesize
	\caption{Comparison of lower bounds for weak Schur numbers}\label{table:2}
\begin{center}
	\begin{small}
	\setlength{\tabcolsep}{3pt}
	\renewcommand{\arraystretch}{1.2}
	\begin{NiceTabular}{*{13}{c}}[vlines]
	\CodeBefore
		\cellcolor{gray!40}{2-2}
		\cellcolor{gray!40}{2-3}
		\cellcolor{gray!40}{2-4}
		\cellcolor{gray!40}{2-5}
		\cellcolor{gray!40}{3-2}
		\cellcolor{gray!40}{3-3}
		\cellcolor{gray!40}{3-4}
		\cellcolor{gray!40}{3-5}
	\Body
		\hline
		\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
		\hline
		\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
		& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} &
			\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
		\hline
		\hyperref[WeakSchur]{\textbf{Our results}}& & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
		\hline
	\end{NiceTabular}
	\end{small}
\end{center}
}
\end{table}

@@

\begin{figure}[tbhp]
{\footnotesize
	\caption{Visualisation of an Abbott and Hanson construction}\label{figure:1}}
\begin{center}

@@

\begin{figure}[tbhp]
{\footnotesize
	\caption{Visualisation of a template-based construction}\label{figure:2}}
\begin{center}
{\footnotesize\textbf{S-template construction}}
\setlength{\tabcolsep}{1.2ex}
\renewcommand{\arraystretch}{1.5}

@@

\begin{table}[tbhp]
{\footnotesize
	\caption{New lower bounds for \(S(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsS}}
\begin{center}
\[
\begin{array}{c}
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,974 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 188\,299 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,272\,730 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 644\,628 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\end{center}
\end{table}

@@

\begin{figure}[tbhp]
{\footnotesize
	\caption{Construction of the weakly sum-free coloring}\label{SchemaWS}}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{small}
\[
\begin{NiceArray}{*{13}{c}}[corners={NW,SW},hvlines,first-row,last-row,first-col]
\CodeBefore
	\cellcolor{green}{1-6}
	\cellcolor{green}{1-7}
	\cellcolor{cyan}{1-8}
	\cellcolor{green}{1-9}
	\cellcolor{cyan}{1-10}
	\cellcolor{cyan}{1-11}
	\cellcolor{cyan}{1-12}
	\cellcolor{green}{1-13}
	\cellcolor{red}{2-1}
	\cellcolor{red}{2-2}
	\cellcolor{red}{2-3}
	\cellcolor{red}{2-4}
	\cellcolor{red}{2-5}
	\cellcolor{red}{2-6}
	\cellcolor{red}{2-7}
	\cellcolor{red}{2-8}
	\cellcolor{red}{2-9}
	\cellcolor{cyan}{2-10}
	\cellcolor{cyan}{2-11}
	\cellcolor{cyan}{2-12}
	\cellcolor{green}{2-13}
	\cellcolor{yellow}{3-1}
	\cellcolor{yellow}{3-2}
	\cellcolor{yellow}{3-3}
	\cellcolor{yellow}{3-4}
	\cellcolor{yellow}{3-5}
	\cellcolor{yellow}{3-6}
	\cellcolor{yellow}{3-7}
	\cellcolor{yellow}{3-8}
	\cellcolor{yellow}{3-9}
	\cellcolor{cyan}{3-10}
	\cellcolor{cyan}{3-11}
	\cellcolor{cyan}{3-12}
	\cellcolor{green}{3-13}
	\cellcolor{yellow}{4-1}
	\cellcolor{yellow}{4-2}
	\cellcolor{yellow}{4-3}
	\cellcolor{yellow}{4-4}
	\cellcolor{yellow}{4-5}
	\cellcolor{yellow}{4-6}
	\cellcolor{yellow}{4-7}
	\cellcolor{yellow}{4-8}
	\cellcolor{yellow}{4-9}
	\cellcolor{cyan}{4-10}
	\cellcolor{cyan}{4-11}
	\cellcolor{cyan}{4-12}
	\cellcolor{green}{4-13}
	\cellcolor{red}{5-1}
	\cellcolor{red}{5-2}
	\cellcolor{red}{5-3}
	\cellcolor{red}{5-4}
	\cellcolor{red}{5-5}
	\cellcolor{red}{5-6}
	\cellcolor{red}{5-7}
	\cellcolor{red}{5-8}
	\cellcolor{red}{5-9}
	\cellcolor{cyan}{5-10}
	\cellcolor{cyan}{5-11}
	\cellcolor{cyan}{5-12}
	\cellcolor{green}{5-13}
	\cellcolor{cyan}{6-10}
	\cellcolor{cyan}{6-11}
	\cellcolor{cyan}{6-12}
	\cellcolor{green}{6-13}
\Body
	& & & & & & \Block{1-8}{\overbrace{\hphantom{---------------------------}}^{\mathcal{T}}} \\
	& & & & & & 1 & 2 & ... & r & r + 1 & ... & q - 1 & q \\
	\Block{5-1}{\mathcal{R} \left\{ \vphantom{\begin{array}{l} . \\ . \\ . \\ . \\ . \\ . \\ . \\  . \end{array}} \right.}
	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + q - 1 & a + q \\
	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + q \\
	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + q \\
	& & & & & & & & & & \Block{1-4}{\underbrace{\hphantom{--------------}}_{\mathcal{C}}} \\
\end{NiceArray}
\]
\end{small}
\end{center}
\end{figure}

@@

\begin{table}[tbhp]
{\footnotesize
	\caption{New lower bounds for  \(\WS(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsWS}}
\begin{center}
\[
\begin{array}{c}
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-5}
		\cellcolor{yellow}{3-2}
		\cellcolor{yellow}{4-3}
		\cellcolor{yellow}{4-4}
	\Body
		n & 8 & 9 & 10 & 11 \\
		4 \, S(n-1) + 2 & 6\,786 & 21\,146 & 71\,214 & 243\,794 \\
		13 \, S(n-2) + 8 & 6\,976 & 22\,056 & 68\,726 & 231\,447 \\
		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 71\,256 & 222\,036 \\
	\end{NiceArray}
	\\ \\
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		4 \, S(n-1) + 2 & 815\,314 & 2\,578\,514 & 8\,045\,162 & 27\,061\,154 \\
		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,380\,172 & 26\,146\,778 \\
		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  27\,074\,400 \\
	\end{NiceArray}
\end{array}
\]
\end{center}
\end{table}

@@

\bibliography{biblio}
\bibliographystyle{siamplain}

@@

\begin{table}[tbhp]
{\footnotesize
	\caption{S-template with width 33 and 4 colors}}
\begin{center}
\begin{small}
\[
\begin{array}{|*{2}{c|}}
	\hline
	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
	\hline
	2 & 2, 5, 14, 15, 25, 26 \\
	\hline
	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
	\hline
	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
	\hline
\end{array}
\]
\end{small}
\end{center}
\end{table}

\begin{table}[tbhp]
{\footnotesize
	\caption{S-template with width 111 and 5 colors}}
\begin{center}
\begin{small}
\[
\begin{array}{|*{2}{c|}}
	\hline
	1 & 1, 5, 8, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103, 106, 110 \\
	\hline
	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54, 101, 104, 109 \\
	\hline
	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55, 100, 107, 108 \\
	\hline
	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
	\hline
	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70,\\
	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85,\\
	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
	\hline
\end{array}
\]
\end{small}
\end{center}
\end{table}

>>>>

\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{dsfont}
\usepackage{MyMnSymbol}

\usepackage[english]{babel}
\usepackage[hyphens]{url}
\usepackage{hyperref}
\hypersetup{hidelinks}
\usepackage[utf8]{inputenc}
\usepackage{siunitx}
\usepackage{float}

\usepackage[table]{xcolor}
\usepackage{multirow}
\usepackage{nicematrix}

\addtolength{\textheight}{108pt} \addtolength{\topmargin}{-60pt}
\oddsidemargin=-6pt \addtolength{\textwidth}{120pt}
\righthyphenmin=2

\renewcommand{\qedsymbol}{\(\square\)}

\newtheorem{definition}{Definition}[section]
\newtheorem{notation}[definition]{Notation}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{computational theorem}[definition]{Computational Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{remark}[definition]{Remark}
\newtheorem{proposition}[definition]{Proposition}

@@

\newcommand\blfootnote[1]{%
  \begingroup
  \renewcommand\thefootnote{}\footnote{#1}%
  \addtocounter{footnote}{-1}%
  \endgroup
}

\title{New lower bounds for Schur and weak Schur numbers}

\author{
Romain Ageron\textsuperscript{a,1}\and
Paul Casteras\textsuperscript{a,1}\and
Thibaut Pellerin\textsuperscript{a,1}\and
Yann Portella\textsuperscript{a,1}\and
Arpad Rimmel\textsuperscript{b,2}\and
Joanna Tomasik\textsuperscript{b,2,}*
}

\date{
	\textsuperscript{a}CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France\\
	\textsuperscript{b}LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France\\[2ex]
	\today
}

\begin{document}

\maketitle

\blfootnote{\textsuperscript{1}These authors contributed equally.}
\blfootnote{\textsuperscript{2}These authors supervised the work of the main authors.}
\blfootnote{*Corresponding author (\tt{joanna.tomasik@centralesupelec.fr})}
\vspace{-5ex}

@@

Keywords: Schur number, Weak Schur number, Ramsey theory, Sum-free partition

MSC 2020: 05D10, 05A17, 11B75, 11P81

@@

\begin{table}[H]
{\footnotesize
	\caption{Comparison of lower bounds for Schur numbers}\label{table:1}
\begin{center}
	\begin{small}
	\setlength{\tabcolsep}{3pt}
	\renewcommand{\arraystretch}{1.2}
	\begin{NiceTabular}{*{13}{c}}[vlines]
	\CodeBefore
		\cellcolor{gray!40}{2-2}
		\cellcolor{gray!40}{2-3}
		\cellcolor{gray!40}{2-4}
		\cellcolor{gray!40}{2-5}
		\cellcolor{gray!40}{2-6}
		\cellcolor{gray!40}{3-2}
		\cellcolor{gray!40}{3-3}
		\cellcolor{gray!40}{3-4}
		\cellcolor{gray!40}{3-5}
		\cellcolor{gray!40}{3-6}
	\Body
		\hline
		\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
		\hline
		\Block{2-1}{State of the art} & 1 & 4 & 13 & 44 & 160 & 536 & 1\,696 & 5\,286 & 17\,694 & 60\,320 & 201\,696 & 637\,856 \\
		& & & & & \cite{Heule2017} & \cite{Fredricksen} & \cite{rowley2021improved} & \cite{RowleyRamsey} & \cite{RowleyRamsey} &
			\cite{RowleyRamsey} & \cite{RowleyRamsey} & \cite{RowleyRamsey} \\
		\hline
		\hyperref[Schur]{\textbf{Our results}}  & & & & & & & & & \textbf{17\,803} & \textbf{60\,948} & \textbf{203\,828} & \textbf{644\,628} \\
		\hline
	\end{NiceTabular}
	\end{small}
\end{center}
}
\end{table}

\begin{table}[H]
{\footnotesize
	\caption{Comparison of lower bounds for weak Schur numbers}\label{table:2}
\begin{center}
	\begin{small}
	\setlength{\tabcolsep}{3pt}
	\renewcommand{\arraystretch}{1.2}
	\begin{NiceTabular}{*{13}{c}}[vlines]
	\CodeBefore
		\cellcolor{gray!40}{2-2}
		\cellcolor{gray!40}{2-3}
		\cellcolor{gray!40}{2-4}
		\cellcolor{gray!40}{2-5}
		\cellcolor{gray!40}{3-2}
		\cellcolor{gray!40}{3-3}
		\cellcolor{gray!40}{3-4}
		\cellcolor{gray!40}{3-5}
	\Body
		\hline
		\(n\) & 1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 & 11 & 12 \\
		\hline
		\Block{2-1}{State of the art} & 2 & 8 & 23 & 66 & 196 & 642 & 2\,146 & 6\,976 & 22\,056 & 70\,778 & 241\,282 & 806\,786 \\
		& & & & & \cite{ELIAHOU2012175} &\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} &
			\cite{RowleyWS} & \cite{RowleyWS} & \cite{RowleyWS} \\
		\hline
		\hyperref[WeakSchur]{\textbf{Our results}}& & & & & & \textbf{646} & & & \textbf{22\,536} & \textbf{71\,256} & \textbf{243\,794} & \textbf{815\,314} \\
		\hline
	\end{NiceTabular}
	\end{small}
\end{center}
}
\end{table}

@@

\begin{figure}[H]
{\footnotesize
	\caption{Visualisation of an Abbott and Hanson construction}\label{figure:1}}
\begin{center}

@@

\begin{figure}[H]
{\footnotesize
	\caption{Visualisation of a template-based construction}\label{figure:2}}
\begin{center}
{\footnotesize\textbf{S-template construction}}
\setlength{\tabcolsep}{1.2ex}
\renewcommand{\arraystretch}{1.5}

@@

\begin{table}[H]
{\footnotesize
	\caption{New lower bounds for \(S(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsS}}
\begin{center}
\[
\begin{array}{c}
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 8 & 9 & 10 & 11 \\
		33 \, S(n-3) + 6 & 5\,286 & 17\,694 & 55\,974 & 174\,444 \\
		111 \, S(n-4) + 43 & 4927 & 17\,803 & 59\,539 & 188\,299 \\
		380 \, S(n-5) + 148 & 5\,088 & 16\,868 & 60\,948 & 203\,828 \\
	\end{NiceArray}
	\\ \\
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-3}
		\cellcolor{yellow}{4-2}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		33 \, S(n-3) + 6 & 587\,505 & 2\,011\,290 & 6\,726\,330 & 21\,272\,730 \\
		111 \, S(n-4) + 43 & 586\,789 & 1\,976\,176 & 6\,765\,271 & 22\,624\,951 \\
		380 \, S(n-5) + 148 & 644\,628 & 2\,008\,828 & 6\,765\,288 & 23\,160\,388 \\
	\end{NiceArray}
\end{array}
\]
\end{center}
\end{table}

@@

\begin{figure}[H]
{\footnotesize
	\caption{Construction of the weakly sum-free coloring}\label{SchemaWS}}
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{small}
\[
\begin{NiceArray}{*{13}{c}}[corners={NW,SW},hvlines,first-row,last-row,first-col]
\CodeBefore
	\cellcolor{green}{1-6}
	\cellcolor{green}{1-7}
	\cellcolor{cyan}{1-8}
	\cellcolor{green}{1-9}
	\cellcolor{cyan}{1-10}
	\cellcolor{cyan}{1-11}
	\cellcolor{cyan}{1-12}
	\cellcolor{green}{1-13}
	\cellcolor{red}{2-1}
	\cellcolor{red}{2-2}
	\cellcolor{red}{2-3}
	\cellcolor{red}{2-4}
	\cellcolor{red}{2-5}
	\cellcolor{red}{2-6}
	\cellcolor{red}{2-7}
	\cellcolor{red}{2-8}
	\cellcolor{red}{2-9}
	\cellcolor{cyan}{2-10}
	\cellcolor{cyan}{2-11}
	\cellcolor{cyan}{2-12}
	\cellcolor{green}{2-13}
	\cellcolor{yellow}{3-1}
	\cellcolor{yellow}{3-2}
	\cellcolor{yellow}{3-3}
	\cellcolor{yellow}{3-4}
	\cellcolor{yellow}{3-5}
	\cellcolor{yellow}{3-6}
	\cellcolor{yellow}{3-7}
	\cellcolor{yellow}{3-8}
	\cellcolor{yellow}{3-9}
	\cellcolor{cyan}{3-10}
	\cellcolor{cyan}{3-11}
	\cellcolor{cyan}{3-12}
	\cellcolor{green}{3-13}
	\cellcolor{yellow}{4-1}
	\cellcolor{yellow}{4-2}
	\cellcolor{yellow}{4-3}
	\cellcolor{yellow}{4-4}
	\cellcolor{yellow}{4-5}
	\cellcolor{yellow}{4-6}
	\cellcolor{yellow}{4-7}
	\cellcolor{yellow}{4-8}
	\cellcolor{yellow}{4-9}
	\cellcolor{cyan}{4-10}
	\cellcolor{cyan}{4-11}
	\cellcolor{cyan}{4-12}
	\cellcolor{green}{4-13}
	\cellcolor{red}{5-1}
	\cellcolor{red}{5-2}
	\cellcolor{red}{5-3}
	\cellcolor{red}{5-4}
	\cellcolor{red}{5-5}
	\cellcolor{red}{5-6}
	\cellcolor{red}{5-7}
	\cellcolor{red}{5-8}
	\cellcolor{red}{5-9}
	\cellcolor{cyan}{5-10}
	\cellcolor{cyan}{5-11}
	\cellcolor{cyan}{5-12}
	\cellcolor{green}{5-13}
	\cellcolor{cyan}{6-10}
	\cellcolor{cyan}{6-11}
	\cellcolor{cyan}{6-12}
	\cellcolor{green}{6-13}
\Body
	& & & & & & \Block{1-8}{\overbrace{\hphantom{---------------------------}}^{\mathcal{T}}} \\
	& & & & & & 1 & 2 & ... & r & r + 1 & ... & q - 1 & q \\
	\Block{5-1}{\mathcal{R} \left\{ \vphantom{\begin{array}{l} . \\ . \\ . \\ . \\ . \\ . \\ . \\  . \end{array}} \right.}
	& a - l & a - l + 1 & ... & a - 1 & a & a + 1 & ... & a + r - 1 & a + r & a + r + 1 & ... & a + q - 1 & a + q \\
	& 2 a - l & ... & ... & ... & 2 a & ... & ... & ... & 2 a + r & ... & ... & ... & 2 a + q \\
	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
	& ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... & ... \\
	& p a - l & ... & ... & ... & p a & ... & ... & ... & p a + r & ... & ... & ... & p a + q \\
	& & & & & & & & & & \Block{1-4}{\underbrace{\hphantom{--------------}}_{\mathcal{C}}} \\
\end{NiceArray}
\]
\end{small}
\end{center}
\end{figure}

@@

\begin{table}[H]
{\footnotesize
	\caption{New lower bounds for  \(\WS(n)\) with \( n \in [\![8,15]\!] \)}\label{LowerBoundsWS}}
\begin{center}
\[
\begin{array}{c}
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-5}
		\cellcolor{yellow}{3-2}
		\cellcolor{yellow}{4-3}
		\cellcolor{yellow}{4-4}
	\Body
		n & 8 & 9 & 10 & 11 \\
		4 \, S(n-1) + 2 & 6\,786 & 21\,146 & 71\,214 & 243\,794 \\
		13 \, S(n-2) + 8 & 6\,976 & 22\,056 & 68\,726 & 231\,447 \\
		42 \, S(n-3) + 24 & 6\,744 & 22\,536 & 71\,256 & 222\,036 \\
	\end{NiceArray}
	\\ \\
	\begin{NiceArray}{cwc{8ex}wc{10ex}wc{10ex}wc{11ex}}[hvlines]
	\CodeBefore
		\cellcolor{yellow}{2-2}
		\cellcolor{yellow}{3-3}
		\cellcolor{yellow}{4-4}
		\cellcolor{yellow}{4-5}
	\Body
		n & 12 & 13 & 14 & 15 \\
		4 \, S(n-1) + 2 & 815\,314 & 2\,578\,514 & 8\,045\,162 & 27\,061\,154 \\
		13 \, S(n-2) + 8 & 792\,332 & 2\,649\,772 & 8\,380\,172 & 26\,146\,778 \\
		42 \, S(n-3) + 24 & 747\,750 & 2\,559\,840 & 8\,560\,800 &  27\,074\,400 \\
	\end{NiceArray}
\end{array}
\]
\end{center}
\end{table}

@@

\bibliographystyle{IEEEtran}
\bibliography{biblio}

@@

\begin{table}[H]
{\footnotesize
	\caption{S-template with width 33 and 4 colors}}
\begin{center}
\begin{small}
\[
\begin{array}{|*{2}{c|}}
	\hline
	1 & 1, 6, 9, 13, 16, 20, 24, 27, 31 \\
	\hline
	2 & 2, 5, 14, 15, 25, 26 \\
	\hline
	3 & 3, 4, 10, 11, 12, 28, 29, 30 \\
	\hline
	4 & 7, 8, 17, 18, 19, 21, 22, 23, 32, 33 \\
	\hline
\end{array}
\]
\end{small}
\end{center}
\end{table}

\begin{table}[H]
{\footnotesize
	\caption{S-template with width 111 and 5 colors}}
\begin{center}
\begin{small}
\[
\begin{array}{|*{2}{c|}}
	\hline
	1 & 1, 5, 8, 12, 14 ,21, 23, 30, 32, 36, 39, 43, 45, 52, 103, 106, 110 \\
	\hline
	2 & 2, 6, 7, 10, 15, 18, 26, 29, 34, 37, 38, 42, 46, 51, 54, 101, 104, 109 \\
	\hline
	3 & 3, 4, 9, 11, 17, 19, 25, 27, 33, 35, 40, 41, 47, 48, 55, 100, 107, 108 \\
	\hline
	4 & 13, 16, 20, 22, 24, 28, 31, 58, 61, 67, 88, 94, 97 \\
	\hline
	5 & 44, 50, 53, 56, 57, 59, 60, 62, 63, 64, 65, 66, 68, 69, 70,\\
	& 71, 72, 73, 74, 75, 76, 77, 78, 79, 80, 81, 82, 83, 84, 85,\\
	& 86, 87, 89, 90, 91, 92, 93, 95, 96, 98, 99, 102, 105, 111 \\
	\hline
\end{array}
\]
\end{small}
\end{center}
\end{table}

\begin{table}[H]
{\footnotesize
	\caption{S-template with width 380 and 6 colors}}
\begin{center}
\begin{small}
\[
\begin{array}{|*{2}{c|}}
	\hline
	1 & 1, 5, 8, 11, 15, 17, 29, 33, 36, 39, 43, 57, 61, 88, 92, \\
	& 106, 110, 113, 116, 120, 132, 134, 138, 141, 144, 148, 150, 154, 157, 160, \\
	& 164, 178, 182, 185, 188, 341, 344, 347, 351, 365, 369, 372, 375, 379\\
	\hline
	2 & 2, 9, 13, 16, 20, 23, 24, 27, 28, 31, 34, 35, 38, 42, 45,\\
	& 49, 53, 60, 67, 71, 78, 82, 89, 96, 100, 104, 107, 111, 114, 115,\\
	& 118, 121, 122, 125, 126, 129, 133, 136, 140, 147, 158, 162, 165, 169, 172,\\
	& 176, 183, 187, 194, 201, 328, 335, 342, 346, 353, 357, 360, 364, 367, 371\\
	\hline
	3 & 3, 4, 12, 14, 19, 25, 30, 32, 40, 41, 47, 48, 58, 91, 101,\\
	& 102, 108, 109, 117, 119, 124, 130, 135, 137, 145, 146, 152, 153, 161, 163,\\
	& 168, 179, 181, 190, 339, 348, 350, 361, 366, 368, 376, 377\\
	\hline
	4 & 6, 7, 10, 18, 21, 22, 26, 37, 46, 50, 51, 54, 65, 70, 79, 84, 95, 98,\\
	& 99, 103, 112, 123, 127, 128, 131, 139, 142, 143, 151, 155, 156, 159,\\
	& 167, 170, 171, 175, 186, 343, 354, 358, 359, 362, 370, 373, 374, 378\\
	\hline
	5 & 44, 52, 55, 56, 59, 62, 63, 64, 66, 68, 69, 72, 73, 74, 75, 76, 77, 80, 81, 83,\\
	&  85, 86, 87, 90, 93, 94, 97, 105, 189, 196, 197, 200, 203, 206, 207, \\
	& 209, 214, 219, 231, 298, 310, 315, 320, 322, 323,  326, 329, 332, 333, 340\\
	\hline
	6 & 149, 166, 173, 174, 177, 180, 184, 191, 192, 193, 195, 198, 199, 202, 204,\\
	& 205, 208, 210, 211, 212, 213, 215, 216, 217, 218, 220, 221, 222, 223, 224,\\
	& 225, 226, 227, 228, 229, 230, 232, 233, 234, 235, 236, 237, 238, 239, 240,\\
	& 241, 242, 243, 244, 245, 246, 247, 248, 249, 250, 251, 252, 253, 254, 255,\\
	& 256, 257, 258, 259, 260, 261, 262, 263, 264, 265, 266, 267, 268, 269, 270,\\
	& 271, 272, 273, 274, 275, 276, 277, 278, 279, 280, 281, 282, 283, 284, 285,\\
	& 286, 287, 288, 289, 290, 291, 292, 293, 294, 295, 296, 297, 299, 300, 301, 302,\\
	& 303, 304, 305, 306, 307, 308, 309, 311, 312, 313, 314, 316, 317, 318, 319, 321,\\
	& 324, 325, 327, 330, 331, 334, 336, 337, 338, 345, 349, 352, 355, 356, 363, 380\\
	\hline
\end{array}
\]
\end{small}
\end{center}
\end{table}
